\documentclass[11pt]{article}
\usepackage{geometry}
\geometry{letterpaper}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
%\usepackage{subfigure}
%\usepackage{float}
\usepackage{multirow}
%\usepackage{fullpage}
\usepackage{hyperref}
%\usepackage[compact]{titlesec} %Reduces the space around headings
\usepackage[parfill]{parskip}    % Activate to begin paragraphs with an empty line rather than an indent
%\usepackage{natbib} %For citations!

\title{ Design Document for COS 333 Project }
\author{Noah Apthorpe, Garrett Disco, Luke Paulsen, Jocelyn Tang, and Natalie Weires}

\begin{document}

\maketitle

\section{The Group}
\par Project name: ``Course Aggregator Tool" (CAT)
\par Project manager: Garrett Disco
\begin{tabbing}
Noah Apthorpe\; \= apthorpe@princeton.edu \\
Garret Disco \> gdisco@princeton.edu \\
Luke Paulsen \> lpaulsen@princeton.edu \\
Jocelyn Tang \> jmtang@princeton.edu \\
Natalie Weires \> nweires@princeton.edu
\end{tabbing}

\section{Overview}
\par The Course Aggregator Tool is an online platform for viewing and querying Princeton course information available at various OIT and Registrar sites. This will help Princeton undergraduates make course selection and scheduling decisions, including long-term course planning. The site is different from other tools such as ICE and the Registrar site in that it will allow easy visualization of all available data on a course, make it easier to compare and rank courses, and provide historical data on older semesters of a course. It is not designed to provide calendar-style scheduling the way ICE is.
\par CAT will provide a graphical interface that will make it easy for users to get a sense of what a course is like and select what information they want to see. It will also provide a way to compare two or more courses side-by-side. The course data displayed will include: professors, class size, class times, ratings (in various categories), written course reviews, P/D/F status, distribution area, and textbooks. It will be possible to search for, rank, and filter courses by any of these categories, either over the whole university or by department or distribution requirement. We will also include a system for rating a course review ``up" or ``down" for its helpfulness.
\par CAT will be built with Python/Django and hosted on Amazon AWS. We will scrape course data periodically (e.g. once per semester) from the Registrar website and store it in a Mongo database. We are still deciding on how to set up the frontend, but it is likely to involve heavy use of Javascript-based tools and Ajax.

\section{Functionality}
CAT has several different possible use cases, all of which involve a comparison of multiple courses.
\par Use case 1: A user wants to find a class fitting a particular kind of description (e.g. ``find a large LA class that is well-reviewed and offered after 11 AM"). The user logs in to CAT, which displays a prominent search box where all of these parameters can be entered (either a selection of fields, or a single text bar with smart interpretation, or both). Once the user has entered the search parameters, the best-matching courses are displayed, from which the user can select one or more courses to view the full data for.
\par Use case 2: A user is only considering a few courses (e.g. COS 333 and COS 402) and wants to compare their ratings in detail. The user opens both courses (by typing the course code into the search box, then opening another search box and repeating the process) and compares them side-by-side with respect to those attributes that they find relevant (e.g. lecture ratings, overall ratings, enrollment numbers, etc.)
\par Use case 3: A user is browsing courses and is considering what to take in future semesters. The user puts in very general search parameters (e.g. all COS classes) and looks at classes from the result list one at a time. When viewing courses, the user activates the ``timeline" option, which brings up past semesters of the course as well as the most recent semester. Then user can then view how course ratings, class size, readings, and so on have changed over time.

\par Core functionality that will be required:
\begin{itemize}
\item Search for and rank courses by one or more categories
\item Display full data for one or more courses from search results
\item Add additional boxes to search for and view courses in
\item Extend a single semester to a timeline for that course
\item Choose which data to display for courses
\end{itemize}

\par Additional features we are considering include:
\begin{itemize}
\item Display textbook costs
\item Predict what future semesters of a class will be like
\item Allow student course reviews to be rated up or down
\item Include prerequisites and certificate requirements
\item Analyze text of course reviews for key terms, positive versus negative, etc.
\item Maintain favorite courses for each student
\end{itemize}

\section{Design}
\par We have decided to use MongoDB for the database because a lot of the data is irregular - for example, classes have different numbers of sections, multiple professors, etc. Each class is a document with fields for each feature: professor, sections, ratings and reviews, pdf status, distribution category, sample readings, grading breakdown, class number, pre-requisites, course description.
\par Our primary source of data is the registrar. We plan to scrape the course offerings website as well as the ratings and reviews, which come from applyweb.com. Much of the data is also available in XML format from an OIT web feed.
% https://webfeeds.princeton.edu/#feed,19
\par We plan to use the Django framework to structure the website. It provides a powerful and well-organized system for accessing the database and sending information to the client.The Django view functions will be used as the interface for interacting with the client side, and we will use the pymongo package (or possibly a more specific Django-Mongo engine) to retrieve information from the database.
\par We plan to use some kind of Javascript (most likely jQuery) for the frontend. This will let us provide an intuitive and interactive user interface, while accessing server-side data efficiently using Ajax requests.

\section{Milestones}
\par Already complete:
\begin{itemize}
\item Set up minimal Django site on localhost
\item Get in contact with OIT and Registrar
\item Produce basic frontend design
\end{itemize}
\par For 3/22:
\begin{itemize}
\item Set up site on AWS or OIT, be able to send data
\item Set up MongoDB, be able to send data
\item Produce a minimal scraper (e.g. get 1 piece of data for a given course)
\item Define frontend API (what does Django need to send and what does Javascript take care of?)
\end{itemize}
\par For 3/29:
\begin{itemize}
\item Have a minimal site (Django + Mongo) up on AWS
\item Define database structure (all categories we will need)
\item Scrape all relevant data for any given course
\item Get a minimal version of the frontend working (Javascript or similar communicating with Django)
\end{itemize}
\par For 4/5:
\begin{itemize}
\item Display single-course data on frontend
\item Scrape data for many courses automatically
\item Search, filter, and rank courses by any category
\item Decide on final frontend design specs
\end{itemize}
\par For 4/12:
\begin{itemize}
\item Implement CAS login wall
\item Display search bar and results on frontend
\item Scrape data for all courses, including corner cases
\item Project prototype ready
\end{itemize}
\par For 4/19:
\begin{itemize}
\item Implement interactive stuff (tabbing and choosing which data to view) on frontend
\item Open multiple course boxes on frontend
\item Test system's protection against basic attacks
\item Store user data on backend
\end{itemize}
\par For 4/26:
\begin{itemize}
\item Finish frontend navigation
\item Implement additional features / categories
\item Deploy for alpha test
\end{itemize}
\par For 5/3:
\begin{itemize}
\item Evaluate alpha test feedback
\item Finish frontend styles / graphics
\item Finish adding features
\item Deploy for beta test
\end{itemize}
\par For 5/10:
\begin{itemize}
\item Finalize software
\item Produce demo presentation
\end{itemize}

\section{Risks}
\begin{itemize}
\item Getting access to data: We may have to meet with OIT or the registrar to scrape the ratings and reviews for courses, since this data requires login information.
\item Changing course numbers: In the case that departments change course numbers, we need to be able to track this for each semester. We can do this by comparing numbers of classes that have the same names over the course of the semester.
\item Integration: Interaction between Django and Mongo is not as throughly structured or documented as it is for relational databases like MySQL. Some experiementation will probably be needed to get this to work.
\end{itemize}

\section{Timeline}
\par Our timeline is posted at \\
\url{http://www.princeton.edu/~nweires/timeline.html}.
\par The timeline (and the rest of our project) can also be viewed on Github at \\
\url{https://github.com/lpaulsen333/cat}.

\end{document}